20220426_main_plot_t_test

### 2022-04-30 exploratory/20220426_main_plot_t_test.Rmd
embedded r codes in the manuscript and completed the results section, close #8

# combine the descriptives, test results, and effect size
full_join(casual_des, casual_t_test, by = "homosexual_dlikelihood_dstandard") %>% 
  full_join(., casual_d, by = "homosexual_dlikelihood_dstandard") %>% 
  kable()
```

>>>>

# combine the descriptives, test results, and effect size
des_t_d <- 
  full_join(casual_des, casual_t_test, by = "homosexual_dlikelihood_dstandard") %>% 
  full_join(., casual_d, by = "homosexual_dlikelihood_dstandard")

# display the results 
des_t_d %>% kable()
```
